Response to Reviewers' Comments

### 2025-02-17 review/review.tex
Add an answer to stabbing ray robustness

	      \answer{TODO what robustness issues and instability ?}

>>>>

	      \answer{The stabbing ray approach can encounter numerical errors when a ray hits a corner, potentially leading to misclassification of intersections, but this is mitigated by using a bounded interval and stable parameter numbering to ensure robustness.}
